Human tissue specific markers

### 2017-06-12 manuscript/manuscript.Rnw
abstract out tissue specific marker tables

@@

@@

<<uterus.specific.markers.table,results="asis",echo=FALSE>>=
temp <- tissue.specific.genes[tissue=="uterus",
                              list(gene,tissue,specificity,gi.max)]
setorder(temp,-gi.max)
setnames(temp,c("Gene","Tissue","Tissue Specificity","Mean Expression"))
print(xtable(temp,
             caption="Uterus specific genes",
             label="tab:uterus_specific_genes"),
      include.rownames=FALSE,
      )
rm(temp)
@

@@

<<placenta.specific.markers.table,results="asis",echo=FALSE>>=
temp <- tissue.specific.genes[tissue=="placenta" & gi.max > 100,
                              list(gene,tissue,specificity,gi.max)]
setorder(temp,-gi.max)
setnames(temp,c("Gene","Tissue","Tissue Specificity","Mean Expression"))
print(xtable(temp,
             caption="Placenta specific genes",label="tab:placenta_specific_genes"),
      include.rownames=FALSE,
      floating=FALSE,
      tabular.environment="longtable"
      )
rm(temp)
@

>>>>

<<genes.table.sanitize,echo=FALSE,results="hide">>=
genes.table.sanitize <- function(str){
    return(str)
}
link.gene.names <- function(gene){
    return(paste0("\\href{http://www.ensembl.org/Homo_sapiens/Gene/Summary?g=",
                  gene,"}{",
                  "\\textit{",xtable.sanitize.text(gene),
                  "}}"))
}
xtable.sanitize.text <- function(str){
    result <- str
    result <- gsub("\\\\", "SANITIZE.BACKSLASH", result)
    result <- gsub("$", "\\$", result, fixed = TRUE)
    result <- gsub(">", "$>$", result, fixed = TRUE)
    result <- gsub("<", "$<$", result, fixed = TRUE)
    result <- gsub("|", "$|$", result, fixed = TRUE)
    result <- gsub("{", "\\{", result, fixed = TRUE)
    result <- gsub("}", "\\}", result, fixed = TRUE)
    result <- gsub("%", "\\%", result, fixed = TRUE)
    result <- gsub("&", "\\&", result, fixed = TRUE)
    result <- gsub("_", "\\_", result, fixed = TRUE)
    result <- gsub("#", "\\#", result, fixed = TRUE)
    result <- gsub("^", "\\verb|^|", result, fixed = TRUE)
    result <- gsub("~", "\\~{}", result, fixed = TRUE)
    result <- gsub("SANITIZE.BACKSLASH", "$\\backslash$",
                   result, fixed = TRUE)
    return(result)
}
source("/home/don/projects/xtable/pkg/R/print.xtable.R")

@@

<<tissue.specific.markers.table,results="hide",echo=FALSE>>=
tissue.specific.markers.table <- function(tissue,legend,min.gi=0) {
    this.tissue <- tissue
    temp <-
        tissue.specific.genes[tissue==this.tissue & gi.max >= min.gi,
                              list(Gene=link.gene.names(gene),
                                   "{Tissue specificity}"=specificity,
                                   "{Mean Expression}"=gi.max)]
    setorder(temp,-`{Mean Expression}`)
    print(xtable(temp,
                 align=c("r","c","S","S[table-format=1.0]"),
                 caption=legend,
                 label=paste0("tab:",tissue,"_specific_genes")),
          sanitize.text.function=genes.table.sanitize,
          include.rownames=FALSE,
          booktabs=TRUE,
          floating=TRUE,
          )
    rm(temp)
}

@@

<<uterus.specific.markers.table,results="asis",echo=FALSE>>=
tissue.specific.markers.table(tissue="uterus",
                              legend="Uterus specific genes")
@

@@

<<placenta.specific.markers.table,results="asis",echo=FALSE>>=
tissue.specific.markers.table(tissue="placenta",
                              legend=
                                  paste0("Placenta specific genes with expression ",
                                         "$\\ge 100$ ordered by median expression in placenta."),
                              min.gi=100
                              )
@
